### 2016-03-05 README.Rmd
svglite doesn't work...yet
vis_guess prototype
vis_guess works now!
addressed [pull request from
Miles](https://github.com/tierneyn/visdat/pull/13).

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  dev = "svglite"
)

@@

@@

@@

I am keen to allow for each cell to be colored according to its type (e.g., strings, factors, integers, decimals, dates, missing data). This is currently being undertaken using functions from Hadley Wickham's `readr` package.

@@

Thank you to Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about vis_dat, and for her code contributions that actually allow the paper to .

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

@@

- **new!!** `vis_guess` has a guess at what the value of each cell. So "10.1" will return "double", and `10.1` will return "double", and 01/01/01 will return "date". Keep in mind that it is a **guess** at what each cell is, so you can't trust this fully. `vis_guess` is made possible thanks to Hadley Wickham's `readr` package - thanks mate!

@@

`vis_guess` takes a guess at what each cell is. It's best illustrated using some messy data, which we'll make here.

messy_vector <- c(TRUE,
                  T,
                  "TRUE",
                  "T",
                  "01/01/01",
                  "01/01/2001",
                  NA,
                  NaN,
                  "NA",
                  "Na",
                  "na",
                  "10",
                  10,
                  "10.1",
                  10.1,
                  "abc",
                  "$%TG")

messy_df <- data.frame(var1 = messy_vector,
                       var2 = sample(messy_vector),
                       var3 = sample(messy_vector))

vis_guess(messy_df)

So here we see that there are many different kinds of data in your dataframe. As an analyst this might be a depressing finding. Compare this to `vis_dat`.

vis_dat(messy_df)

Where you'd just assume your data is wierd because it's all factors - or worse, not notice that this is a problem.

At the moment `vis_guess` is slow as - take this into consideration when you are using it on data with more than 1000 rows. We're looking into ways of making it faster, potentially using methods from the `parallel` package, or writing some c++ code.

@@

@@

Thank you to Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about vis_dat, and for her code contributions that remove a lot of testing errors.

Thank you to Hadley Wickham for suggesting the use of the internals of `readr` to make `vis_guess` work.

Thank you to Miles McBain for his suggestions on how to improve vis guess. This resulted in making it at least 2-3 times faster.
